Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-07-03 survey/survey.tex
comment out the graphical language in section 4. re-line up the example, to make it more readable.

Idea: thinking in the 3D way; we have collections of towers of
blocks. Every 1-combinator involves touching some blocks, swapping
them around, etc. Two 1-combinators are equivalent if they touch the
same blocks the same number of times. ??

@@

@@

\AgdaDatatype{⇔}\AgdaSpace{}%

@@

\AgdaInductiveConstructor{⊕}\AgdaSpace{}%

@@

\AgdaInductiveConstructor{◎}\AgdaSpace{}%

@@

\AgdaInductiveConstructor{⊕}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}\<%
\>[1]\AgdaFunction{⇔⟨}\AgdaSpace{}%

@@

\AgdaInductiveConstructor{⊡}\AgdaSpace{}%

@@

\AgdaFunction{⟩}\<%
\>[1][@{}l@{\AgdaIndent{0}}]%
\AgdaInductiveConstructor{⊕}\AgdaSpace{}%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{⊕}\AgdaSpace{}%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{⊕}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}\<%

@@

\>[1]\AgdaFunction{⇔⟨}\AgdaSpace{}%

@@

\AgdaFunction{⟩}\<%
\>[1][@{}l@{\AgdaIndent{0}}]%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\>[44]\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{⊕}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}\<%

@@

\>[1]\AgdaFunction{⇔⟨}\AgdaSpace{}%

@@

\AgdaFunction{⟩}\<%
\>[1][@{}l@{\AgdaIndent{0}}]%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\>[42]\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{⊕}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}\<%

@@

\>[1]\AgdaFunction{⇔⟨}\AgdaSpace{}%

@@

\AgdaFunction{⟩}\<%
\>[1][@{}l@{\AgdaIndent{0}}]%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\>[28]\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{⊕}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}\<%

@@

\>[1]\AgdaFunction{⇔⟨}\AgdaSpace{}%

@@

\AgdaFunction{⟩}\<%
\>[1][@{}l@{\AgdaIndent{0}}]%
\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\>[22]\AgdaInductiveConstructor{◎}\AgdaSpace{}%
\AgdaInductiveConstructor{⊕}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}\<%

@@

\>[1]\AgdaFunction{⇔⟨}\AgdaSpace{}%

@@

\AgdaFunction{⟩}\<%

@@

\>[1][@{}l@{\AgdaIndent{0}}]%

@@

\AgdaFunction{▤}\AgdaSymbol{)}\<%

@@

>>>>

We can do for the level-2 combinators the same as was done for level-1:
create a programming language with these combinators as fundamental
constants, typed by level-1 combinators. But we can do more, as these
new combinators are exactly rewrites for level-1 programs.  Thus,
it is possible to create

%%%%%%%%%
% \subsection{Graphical Language}
% 
% Idea: thinking in the 3D way; we have collections of towers of
% blocks. Every 1-combinator involves touching some blocks, swapping
% them around, etc. Two 1-combinators are equivalent if they touch the
% same blocks the same number of times. ??

@@

\renewcommand{\AgdaIndentSpace}{\;\;}
\setlength\mathindent{0.5em}

\begin{samepage}

@@

\AgdaOperator{\AgdaDatatype{⇔}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaInductiveConstructor{⊕}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaInductiveConstructor{⊕}}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}%
\>[75]\AgdaOperator{\AgdaFunction{⇔⟨}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaInductiveConstructor{⊡}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaFunction{⟩}}\<%

@@

\AgdaOperator{\AgdaInductiveConstructor{⊕}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{⊕}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{⊕}}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}%
\>[75]\AgdaOperator{\AgdaFunction{⇔⟨}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaFunction{⟩}}\<%

@@

\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\>[44]\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{⊕}}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}%
\>[75]\AgdaOperator{\AgdaFunction{⇔⟨}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaFunction{⟩}}\<%

@@

\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\>[42]\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{⊕}}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}%
\>[75]\AgdaOperator{\AgdaFunction{⇔⟨}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaFunction{⟩}}\<%

@@

\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\>[28]\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{⊕}}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}%
\>[75]\AgdaOperator{\AgdaFunction{⇔⟨}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaFunction{⟩}}\<%

@@

\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\>[22]\AgdaOperator{\AgdaInductiveConstructor{◎}}\AgdaSpace{}%
\AgdaOperator{\AgdaInductiveConstructor{⊕}}\AgdaSpace{}%
\AgdaInductiveConstructor{swap₊}\AgdaSymbol{))}%
\>[75]\AgdaOperator{\AgdaFunction{⇔⟨}}\AgdaSpace{}%

@@

\AgdaOperator{\AgdaFunction{⟩}}\<%

@@

@@

\AgdaOperator{\AgdaFunction{▤}}\AgdaSymbol{)}\<%

@@

\end{samepage}

\renewcommand{\AgdaIndentSpace}{\AgdaSpace{}$\;\;$}
